Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-15 paper/paper.tex
Added a citation.
Added a reference to a citation.

Each of Larry Kagan's sculptures consists of a metal structure
composed of bent rods of metal mounted to a wall and illuminated by
a bright light from a carefully chosen location. The eye is drawn to
the shadow produced this way, which forms a familiar image, while the
rods themselves often have no obvious pattern. In the simplest case,
the shadow image is a line drawing and the rods are attached to the
wall at several points. For example, the piece ``Frankfurt Chair'' is
like this. Kagan has created many variations on this idea including
incorporating some of the bent rods in the recognizable image while
most of the image is formed by the shadow, as seen in ``Beach Chair''.
``Intersection of Two Circles'' shows that a sculpture composed of rods
can have a solid shadow with a geometric shape. The light source can
be on the ceiling cented over the piece or be off to one side as it
is in ``At''. With the light source on one side the shadow falls
predominantly on the side of the sculpture. Despite the fact that a
single small bright light source is installed to cast the shadow for
each sculpture, soft egdes of the shadow are noticeable in many of
these works. In ``Mosquito I'', Kagan uses this effect in a dramatic
way; the image present in the shadow of this sculpture is a mosquito
with its own shadow cast by an imaginary light source. In order to
make the distinction obvious, Kagan allowed soft shadow edges to show
in the portion of the image corresponding to the imaginary shadow of
the mosquito, but created the image of the mosquito with dark
hard-edged shadows.

@@

\end{appendices}
% ftp://ftp.ams.org/ams/amsrefs/amsrdoc.pdf for amsrefs documentation
\begin{bibdiv}
 \begin{biblist}
  \bib{Dasgupta}{book}{
   title={Algorithms},
   author={Dasgupta, Sanjoy},
   author={Papadimitriou, Christos},
   author={Vazirani, Umesh},
   publisher={McGraw-Hill Education},
   address={New York},
   year={2006}  
  }
  \bib{pyOpenGL}{webpage}{
   title={PyOpenGL Documentation},
   url={http://pyopengl.sourceforge.net/documentation/},
   accessdate={2015-10}
  }
  \bib{gitrepo}{webpage}{
   title={Genetic Algorithms for Shadow Sculptures},
   author={Chris Chappell},
   author={James Hoctor},
   url={https://github.com/chappc/Math-Senior-Research},
   accessdate={2015-12}
  }
  \bib{cylindermagic}{webpage}{
   title={Rendering a Cylinder Between Two Points in OpenGL},
   author={Parris, Joel},
   url={http://lifeofaprogrammergeek.blogspot.com/2008/07/rendering-cylinder-between-two-points.html},
   accessdate={2015-10}
  }
 \end{biblist}

>>>>

Each of Larry Kagan's sculptures consists of a metal structure
composed of bent rods of metal mounted to a wall and illuminated by
a bright light from a carefully chosen location. The eye is drawn to
the shadow produced this way, which forms a familiar image, while the
rods themselves often have no obvious pattern. In the simplest case,
the shadow image is a line drawing and the rods are attached to the
wall at several points. For example, the piece ``Frankfurt Chair'' is
like this. Kagan has created many variations on this idea including
incorporating some of the bent rods in the recognizable image while
most of the image is formed by the shadow, as seen in ``Beach Chair''.
``Intersection of Two Circles'' shows that a sculpture composed of rods
can have a solid shadow with a geometric shape. The light source can
be on the ceiling cented over the piece or be off to one side as it
is in ``At''. With the light source on one side the shadow falls
predominantly on the side of the sculpture. Despite the fact that a
single small bright light source is installed to cast the shadow for
each sculpture, soft egdes of the shadow are noticeable in many of
these works. In ``Mosquito I'', Kagan uses this effect in a dramatic
way; the image present in the shadow of this sculpture is a mosquito
with its own shadow cast by an imaginary light source. In order to
make the distinction obvious, Kagan allowed soft shadow edges to show
in the portion of the image corresponding to the imaginary shadow of
the mosquito, but created the image of the mosquito with dark
hard-edged shadows. All of these sculptures (with the exception of ``At'') can be viewed on Larry Kagan's website \cite{Kagan}.

@@

\end{appendices}
% ftp://ftp.ams.org/ams/amsrefs/amsrdoc.pdf for amsrefs documentation
\begin{bibdiv}
 \begin{biblist}
  \bib{Dasgupta}{book}{
   title={Algorithms},
   author={Dasgupta, Sanjoy},
   author={Papadimitriou, Christos},
   author={Vazirani, Umesh},
   publisher={McGraw-Hill Education},
   address={New York},
   year={2006}  
  }
  \bib{pyOpenGL}{webpage}{
   title={PyOpenGL Documentation},
   url={http://pyopengl.sourceforge.net/documentation/},
   accessdate={2015-10}
  }
  \bib{gitrepo}{webpage}{
   title={Genetic Algorithms for Shadow Sculptures},
   author={Chris Chappell},
   author={James Hoctor},
   url={https://github.com/chappc/Math-Senior-Research},
   accessdate={2015-12}
  }
  \bib{cylindermagic}{webpage}{
   title={Rendering a Cylinder Between Two Points in OpenGL},
   author={Parris, Joel},
   url={http://lifeofaprogrammergeek.blogspot.com/2008/07/rendering-cylinder-between-two-points.html},
   accessdate={2015-10}
  }
  \bib{opengl-tutorial}{webpage}{
   title={opengl-tutorial},
   url={http://www.opengl-tutorial.org/},
   accessdate={November 2015}
  }
  \bib{Kagan}{webpage}{
   title={Larry Kagan Sculpture},
   url={http://larrykagansculpture.com/},
   accessdate={October 2015}
  }
 \end{biblist}
